 extracting environmenal and oceanographic variables

### 2023-05-15 03_environ_var.Rmd
removed code
deleted unused packages and test HYCOM code

---
title: " extracting environmenal and oceanographic variables"
output: html_document
date: "2022-11-06"
---

Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
#library(raster)
library(terra)
library(PAMpal)
library(PAMmisc)
#library(marmap)
library(rerddap)
```

@@

For each buoy, the value of each environmental variable will be added to each track point based on Lat, Long, and UTC.
Data only need to be downloaded once. After that, can refer to the file in the external hard drive ("D:").

@@

```{r}
## HYCOM function above stops at buoys 07 and 08, need to manually run it here. FIX!!
test08 <- matchEnvData(as.data.frame(tracks_SS_08), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

thermData08 <- bind_rows(lapply(test08, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

tracks_SS_08 <- cbind(tracks_SS_08, thermData08)
```

>>>>

---
title: " extracting environmenal and oceanographic variables"
output: html_document
date: "2022-11-06"
---
For each buoy, the value of each environmental variable will be added to each track point based on Lat, Long, and UTC.
Data only need to be downloaded once. After that, can refer to the file in the external hard drive ("D:").

This takes about 2.5 hours to execute completely!

Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
library(terra)
library(PAMpal)
library(PAMmisc)
library(rerddap)
```

@@

@@

# runs hycom variable download and bind for one drift. can ignore if above works.
```{r}
## HYCOM function above stops at buoys 07 and 08, need to manually run it here. FIX!!
#test08 <- matchEnvData(as.data.frame(tracks_SS_08), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

#thermData08 <- bind_rows(lapply(test08, function(x) {
#    # do thermo calcs
#    result <- calcThermoVars(x$matchDepth, x$water_temp)
#    # get specific values
#    result$temp400 <- x$water_temp[x$matchDepth == 400]
#    result$sal400 <- x$salinity[x$matchDepth == 400]
#    result
#}))

#tracks_SS_08 <- cbind(tracks_SS_08, thermData08)
```
